---
title: "Welcome to Presentation!"
author: "Sagar Srinivas"
date: "09/30/2017"
output: 
  revealjs::revealjs_presentation:
    self_contained: false
    reveal_plugins: ["search", "zoom", "notes", "chalkboard", "menu"]
    reveal_options:
      chalkboard: 
        theme: chalkboard
        toggleNotesButton: true
      menu:
        numbers: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! 



## Slide with Bullets

- This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
- When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

<aside class="notes">
Here are some notes.
</aside>

## Slide with R Output

```{r cars, echo = TRUE}
head(cars,5)
summary(cars)
```

## Slide with Plot

```{r qplot, fig.width=6, fig.height=6, message=FALSE}
# Quick summary and plot
library(ggplot2)
qplot(speed, dist, data = cars) + geom_smooth()
```

